Comment: Inferring Trade Costs from Trade Booms and Trade Busts

### 2017-09-15 Paper/Manuscript.tex
Changement du texte et des tables

\toprule
{}&{Contribution of growth in output}&{Contribution of growth in income similarity}&{Contribution of change in trade cost measure}&{Contribution of change in multilateral factors}&{Average growth of bilateral trade flows} \tabularnewline
\midrule\addlinespace[1.5ex]
&\multicolumn{5}{c}{JMN 2011} \tabularnewline
GDP-weighted&215&-6&275&-13&470 \tabularnewline
Unweighted&193&5&283&-15&466 \tabularnewline
\midrule &\multicolumn{5}{c}{JMN by country, unweighted} \tabularnewline
FRA&165&7&122&-13&281 \tabularnewline
UK&175&7&96&-14&264 \tabularnewline
USA&289&-33&195&-11&441 \tabularnewline
Average&216&-7&272&-12&469 \tabularnewline
\midrule &\multicolumn{5}{c}{JMN by country, GDP-weighted} \tabularnewline
FRA&196&-11&127&-10&302 \tabularnewline
UK&201&-4&69&-11&256 \tabularnewline
USA&274&-25&192&-8&433 \tabularnewline
Average&227&-12&254&-10&460 \tabularnewline
\midrule &\multicolumn{5}{c}{Our method} \tabularnewline
FRA&202&-27&77&-6&245 \tabularnewline
UK&202&-16&67&-8&244 \tabularnewline
USA&202&43&89&-7&327 \tabularnewline
Unweighted average&202&-3&137&-7&329 \tabularnewline
GDP-weighted average&202&13&126&-7&333 \tabularnewline
\bottomrule \addlinespace[1.5ex]

@@

\toprule
{}&{Contribution of growth in output}&{Contribution of growth in income similarity}&{Contribution of change in trade cost measure}&{Contribution of change in multilateral factors}&{Average growth of bilateral trade flows} \tabularnewline
\midrule\addlinespace[1.5ex]
&\multicolumn{5}{c}{JMN 2011} \tabularnewline
GDP-weighted&350&6&230&-28&558 \tabularnewline
Unweighted&355&4&284&-35&608 \tabularnewline
\midrule &\multicolumn{5}{c}{JMN by country, unweighted} \tabularnewline
FRA&350&3&318&-30&641 \tabularnewline
UK&297&11&227&-29&507 \tabularnewline
USA&341&9&180&-23&507 \tabularnewline
Average&350&6&224&-27&554 \tabularnewline
\midrule &\multicolumn{5}{c}{JMN by country, GDP-weighted} \tabularnewline
FRA&347&2&259&-21&587 \tabularnewline
UK&315&-12&219&-20&502 \tabularnewline
USA&342&10&161&-18&495 \tabularnewline
Average&347&9&184&-21&519 \tabularnewline
\midrule &\multicolumn{5}{c}{Our method} \tabularnewline
FRA&347&-1&317&-16&648 \tabularnewline
UK&347&-46&236&-15&522 \tabularnewline
USA&347&0&192&-13&526 \tabularnewline
Unweighted average&347&7&254&-16&592 \tabularnewline
GDP-weighted average&347&2&203&-14&538 \tabularnewline
\bottomrule \addlinespace[1.5ex]

@@

Tables \ref{glob1} and \ref{glob2} highlight how much the decomposition
between the decrease in trade costs and the income growth depends on the aggregation technique. When we use the microfounded aggregation method,\footnote{We selected the (GDP-weighted) average of our measure in order
to allow a clear comparison with Jacks \textit{et al.}'s results. There
is of course no rational for such a summary statistic, but the
results for France, the UK and the USA assure that the main
conclusion of this exercice does not depend on averaging over
countries.} 
growth in output is the main driving force behind both waves of growth in
international trade, contributing to about 56\% (203/365) in
the first wave and 66\% (361/545) in the second one. It is no coincidence
if these results are very similar to the ones in table \ref{OR}: 60\% (71/107) in the first globalization and 74\% (183/246) in the second one.
Insofar as a measure of
trade costs is defined residually as everything that explains
differences between domestic and international trade flows, it
is bound to reword the information contained in an openness
ratio.

>>>>

\toprule
{1870-1913}&{Contribution of growth in output}&{Contribution of growth in income similarity}&{Contribution of change in trade cost measure}&{Contribution of change in multilateral factors}&{Average growth of bilateral trade flows} \tabularnewline
\midrule\addlinespace[1.5ex]
&\multicolumn{5}{c}{JMN 2011} \tabularnewline
Unweighted&193&5&283&-15&466 \tabularnewline
\textbf{GDP-weighted}&\textbf{215}&\textbf{-6}&\textbf{275}&\textbf{-13}&\textbf{470} \tabularnewline

\midrule &\multicolumn{5}{c}{JMN by country, unweighted} \tabularnewline
FRA&165&7&122&-13&281 \tabularnewline
UK&175&7&96&-14&264 \tabularnewline
USA&289&-33&195&-11&441 \tabularnewline
Average&216&-7&272&-12&469 \tabularnewline
\midrule &\multicolumn{5}{c}{JMN by country, GDP-weighted} \tabularnewline
FRA&196&-11&127&-10&302 \tabularnewline
UK&201&-4&69&-11&256 \tabularnewline
USA&274&-25&192&-8&433 \tabularnewline
Average&227&-12&254&-10&460 \tabularnewline
\midrule &\multicolumn{5}{c}{Our method} \tabularnewline
FRA&202&-27&77&-6&245 \tabularnewline
UK&202&-16&67&-8&244 \tabularnewline
USA&202&43&89&-7&327 \tabularnewline
Unweighted average&202&-3&137&-7&329 \tabularnewline
\textbf{GDP-weighted average}&\textbf{202}&\textbf{13}&\textbf{126}&\textbf{-7}&\textbf{333} \tabularnewline
\bottomrule \addlinespace[1.5ex]

@@

\toprule
{1950-2000}&{Contribution of growth in output}&{Contribution of growth in income similarity}&{Contribution of change in trade cost measure}&{Contribution of change in multilateral factors}&{Average growth of bilateral trade flows} \tabularnewline
\midrule\addlinespace[1.5ex]
&\multicolumn{5}{c}{JMN 2011} \tabularnewline
Unweighted&355&4&284&-35&608 \tabularnewline
\textbf{GDP-weighted}&\textbf{350}&\textbf{6}&\textbf{230}&\textbf{-28}&\textbf{558} \tabularnewline
\midrule &\multicolumn{5}{c}{JMN by country, unweighted} \tabularnewline
FRA&350&3&318&-30&641 \tabularnewline
UK&297&11&227&-29&507 \tabularnewline
USA&341&9&180&-23&507 \tabularnewline
Average&350&6&224&-27&554 \tabularnewline
\midrule &\multicolumn{5}{c}{JMN by country, GDP-weighted} \tabularnewline
FRA&347&2&259&-21&587 \tabularnewline
UK&315&-12&219&-20&502 \tabularnewline
USA&342&10&161&-18&495 \tabularnewline
Average&347&9&184&-21&519 \tabularnewline
\midrule &\multicolumn{5}{c}{Our method} \tabularnewline
FRA&347&-1&317&-16&648 \tabularnewline
UK&347&-46&236&-15&522 \tabularnewline
USA&347&0&192&-13&526 \tabularnewline
Unweighted average&347&7&254&-16&592 \tabularnewline
\textbf{GDP-weighted average}&\textbf{347}&\textbf{2}&\textbf{203}&\textbf{-14}&\textbf{538} \tabularnewline
\bottomrule \addlinespace[1.5ex]

@@

Tables \ref{glob1} and \ref{glob2} highlight how much the decomposition
between the decrease in trade costs and the income growth depends on the aggregation technique. When we use the microfounded aggregation method,\footnote{We selected the (GDP-weighted) average of our measure in order
to allow a clear comparison with Jacks \textit{et al.}'s results. There
is of course no rational for such a summary statistic, but the
results for France, the UK and the USA assure that the main
conclusion of this exercice does not depend on averaging over
countries.} 
growth in output is the main driving force behind both waves of growth in international trade, contributing to about 60\% (202/333) in the first wave and 66\% (361/545) in the second one. Contrast this with Jack  \textit{et al.}'s results for this sample, respectively 46\% and 63\%.
It is no coincidence if, despite the sample change, these results are similar to the ones in table \ref{OR}: 62\% (113/182) in the first globalization and 74\% (183/246) in the second one.

Insofar as a measure of trade costs is defined residually as everything that explains differences between domestic and international trade flows, it is bound to reword the information contained in an openness ratio.
